---
title             : "Supplemental for Socioeconomic status and adolescent brain responses to peer feedback: Testing the impact on negative affect"
shorttitle    : "SES & brain responses to peer feedback"

bibliography      : "BUDS.bib"
floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man, donotrepeattitle"
csl               : 'biological-psychiatry.csl'
documentclass     : "apa7"
output            : papaja::apa6_pdf
    
editor_options: 
  markdown: 
    wrap: sentence
    
header-includes:
  - \AtBeginDocument{\let\maketitle\relax}
  
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \addtolength{\tabcolsep}{6pt}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \usepackage{caption} # Makes figures and table starts with S as in Figure S1.
  - \DeclareCaptionLabelFormat{Sformat}{#1 S#2}     
  - \captionsetup[table]{labelformat=Sformat}  
  - \captionsetup[figure]{labelformat=Sformat} 
  
  - \raggedbottom
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{phv} % Use Helvetica for serif
  - \renewcommand{\sfdefault}{phv} % Use Helvetica for sans-serif
  - \usepackage{mathastext}          # Make math text Helvetica
---

```{r analysis-preferences}
knitr::opts_chunk$set(set.seed(312), warning=FALSE, message=FALSE, include=FALSE, papaja.title_page = FALSE) # default chunk options
options(width=80, Ncpus = 6, mc.cores=6, max.print=1000000, scipen = 999) # RStudio console options: set width, multiple cores, and do not use scientific notation
rm(list=ls())     #Remove everything from environment
cat("\014")       #Clear Console

  library(haven)      #helps import stata
  library(here)       #nice file paths
  library(psych)      #used for statistical analyses
  library(Hmisc)
  library(purrr)
  library(haven)      #to import SPSS files
# Models
  library(lmerTest)
  library(glmmTMB)
# Plotting
  library(ggplot2)    #creates plots
  library(ggpubr)
  library(ggeffects)
  library(sjPlot)
  library(interactions)
  library(emmeans) # testing simple slopes
    
  library(eegUtils)
  library(gridExtra)
    
  library(Rmisc)
  library(grid)
  library(broom.mixed)

# General tools
  library(tidyverse)  #plotting/cleaning, etc.
  library(papaja)
  library(workflowr)  #helps with workflow

here <- here::here
r_refs("BUDS.bib")
```

```{r Load data}
here::i_am("BUDS_manuscript_working.Rmd")

load(file=here::here("../data/BUDS_do02.RData")) # ERP and self-report data
load(file=here("../data/BUDS_behavior.RData")) # ERP behavioral data
load(file=here("../data/BUDS_do03_gaplots.RData")) # Grand average data
spearman_brown_raw <- read.csv(file=here("../tables/spearman_brown.csv")) # Internal consistency table
```

```{r Functions}
# from https://www.r-bloggers.com/2020/07/create-a-publication-ready-correlation-matrix-with-significance-levels-in-r/

round3 <- function(var) {
  sprintf("%.3f",var)
}

correlation_matrix <- function(df,
                               type = "pearson",
                               digits = 3,
                               decimal.mark = ".",
                               use = "all",
                               show_significance = TRUE,
                               replace_diagonal = FALSE,
                               replacement = ""){
  
  # check arguments
  stopifnot({
    is.numeric(digits)
    digits >= 0
    use %in% c("all", "upper", "lower")
    is.logical(replace_diagonal)
    is.logical(show_significance)
    is.character(replacement)
  })
  # we need the Hmisc package for this
  require(Hmisc)
  
  # retain only numeric and boolean columns
  isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
  if (sum(!isNumericOrBoolean) > 0) {
    cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
  }
  df = df[isNumericOrBoolean]
  
  # transform input data frame to matrix
  x <- as.matrix(df)
  
  # run correlation analysis using Hmisc package
  correlation_matrix <- Hmisc::rcorr(x, type = )
  R <- correlation_matrix$r # Matrix of correlation coeficients
  p <- correlation_matrix$P # Matrix of p-value
  
  # transform correlations to specific character format
  Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)
  
  # if there are any negative numbers, we want to put a space before the positives to align all
  if (sum(R < 0) > 0) {
    Rformatted = ifelse(R > 0, paste0(' ', Rformatted), Rformatted)
  }
  
  # add significance levels if desired
  if (show_significance) {
    # define notions for significance levels; spacing is important.
    stars <- ifelse(is.na(p), "   ", ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "*  ", "   "))))
    Rformatted = paste0(Rformatted, stars)
  }
  # build a new matrix that includes the formatted correlations and their significance stars
  Rnew <- matrix(Rformatted, ncol = ncol(x))
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep =" ")
  
  # replace undesired values
  if (use == 'upper') {
    Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (use == 'lower') {
    Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (replace_diagonal) {
    diag(Rnew) <- replacement
  }
  
  return(Rnew)
}

lmer_adi_interaction_table <- function(data) {
  new_model <- data.frame(model = c("Both","Like","Dislike"),
                            beta = NA, 
                            p = NA)
new_model$beta <- c(broom.mixed::tidy(lmer(formula = ERP ~ Feedback*Voting*ADI_NATRANK_c + (1 | ID), REML=TRUE, data = data))[8,4], broom.mixed::tidy(lmer(formula = ERP ~ Feedback*ADI_NATRANK_c + (1 | ID), REML=TRUE, data = filter(data, Voting=="Like")))[4,4],
                        broom.mixed::tidy(lmer(formula = ERP ~ Feedback*ADI_NATRANK_c + (1 | ID), REML=TRUE, data = filter(data, Voting=="Dislike")))[4,4])

new_model$p <- c(broom.mixed::tidy(lmer(formula = ERP ~ Feedback*Voting*ADI_NATRANK_c + (1 | ID), REML=TRUE, data = data))[8,8], broom.mixed::tidy(lmer(formula = ERP ~ Feedback*ADI_NATRANK_c + (1 | ID), REML=TRUE, data = filter(data, Voting=="Like")))[4,8],
                        broom.mixed::tidy(lmer(formula = ERP ~ Feedback*ADI_NATRANK_c + (1 | ID), REML=TRUE, data = filter(data, Voting=="Dislike")))[4,8])
new_model
}

plot_stats <- function(model, var) {
  temp_stats <- tidy(model) %>% 
    dplyr::filter(term==var) %>%
    dplyr::select(estimate,p.value) %>%
    round3(.)
  paste0("b = ", temp_stats[1], ", p = ", temp_stats[2])
}
```

# Supplemental for *Socioeconomic status and adolescent brain responses to peer feedback: Testing the impact on negative affect*

# Methods and Materials

## Participants

Informed assent and consent were obtained from the adolescent and parent, respectively, and adolescents 18 years or older provided consent.
General inclusion criteria included: (a) Tanner Stage $\ge$ 3 [@tannerClinicalLongitudinalStandards1985], (b) parental and child fluency in English, (c) Wechsler Abbreviated Scale of Intelligence-II (WASI-II) \> 85 [@wechslerWechslerAbbreviatedScale2018], (d) ownership of a personal smartphone (android or iOS), and (e) right-handedness.
General exclusion criteria included: (a) history of head injury or neurological disorders, (b) current moderate or severe substance use disorder, and (c) lifetime history of bipolar or psychotic disorders, oppositional defiant disorder, conduct disorder, organic mental disorder, or developmental disorder.

```{r, include=TRUE, dpi=400, fig.cap="Topographic maps of RewP and P300 to high-value peer acceptance, high-value peer rejection, high-value peer acceptance relative to high-value peer rejection."}

chanlocs <- eegUtils::electrode_locations(read.csv(here::here('../data/topo_plots/chanlocs32.csv')), montage="biosemi64")
ga_acc <- read.delim(here('../data/topo_plots/ga_highvalue_acceptance_AA (Acc-Acc).txt'))%>%
  pivot_longer(cols=c(-time),
               values_to ="amplitude", names_to="electrode")
ga_rej <- read.delim(here('../data/topo_plots/ga_highvalue_rejection_AR (Acc-Rej).txt'))%>%
  pivot_longer(cols=c(-time),
               values_to ="amplitude", names_to="electrode")
ga_diff <- read.delim(here('../data/topo_plots/ga_highvalue_acc_rej_difference_BIN5=B1-B2.txt'))%>%
  pivot_longer(cols=c(-time),
               values_to ="amplitude", names_to="electrode")

scaling_factor=0.45
# Create grobs for the column titles

title_rewp <- textGrob("RewP", gp=gpar(fontsize=14, fontface="bold"))
title_p300 <- textGrob("P300", gp=gpar(fontsize=14, fontface="bold"))

title_acc <- textGrob("Acceptance", gp=gpar(fontsize=14, fontface="bold"), rot=90)
title_rej <- textGrob("Rejection", gp=gpar(fontsize=14, fontface="bold"), rot=90)
title_diff <- textGrob("Acceptance > \nRejection", gp=gpar(fontsize=14, fontface="bold"), rot=90)

chanlocs <- chanlocs %>%
  mutate(electrode = case_match(electrode, "Poz" ~ "POz",
                          .default=electrode))

chanlocs2 <- chanlocs %>%
  mutate(electrode = ifelse(chanlocs$electrode %in% c("Pz", "Cz"), 
                             chanlocs$electrode, 
                             NA))


plot1 <- topoplot(ga_acc,time_lim=c(150,275), chanLocs=chanlocs, contour=TRUE, interp_limit="skirt", chan_marker="none", scaling=scaling_factor, fill_title="", verbose=FALSE) +
 annotate("text", x=1, y=45, label = "Fz", color = "black", size=3) +
 annotate("text", x=1, y=0, label = "Cz", color = "black", size=3) +
  annotate("text", x=1, y=-45, label = "Pz", color = "black", size=3)
plot2 <- topoplot(ga_acc,time_lim=c(275,425), chanLocs=chanlocs, contour=TRUE, interp_limit="skirt", chan_marker="none", scaling=scaling_factor, verbose=FALSE) +
 annotate("text", x=1, y=45, label = "Fz", color = "black", size=3) +
 annotate("text", x=1, y=0, label = "Cz", color = "black", size=3) +
  annotate("text", x=1, y=-45, label = "Pz", color = "black", size=3)

plot3 <- topoplot(ga_rej,time_lim=c(150,275), chanLocs=chanlocs, contour=TRUE, interp_limit="skirt", chan_marker="none", scaling=scaling_factor, fill_title="", verbose=FALSE) +
 annotate("text", x=1, y=45, label = "Fz", color = "black", size=3) +
 annotate("text", x=1, y=0, label = "Cz", color = "black", size=3) +
  annotate("text", x=1, y=-45, label = "Pz", color = "black", size=3)
plot4 <- topoplot(ga_rej,time_lim=c(275,425), chanLocs=chanlocs, contour=TRUE, interp_limit="skirt", chan_marker="none", scaling=scaling_factor, verbose=FALSE) +
 annotate("text", x=1, y=45, label = "Fz", color = "black", size=3) +
 annotate("text", x=1, y=0, label = "Cz", color = "black", size=3) +
  annotate("text", x=1, y=-45, label = "Pz", color = "black", size=3)

plot5 <- topoplot(ga_diff,time_lim=c(150,275), chanLocs=chanlocs, contour=TRUE, interp_limit="skirt", chan_marker="none", scaling=scaling_factor, fill_title="", verbose=FALSE) +
 annotate("text", x=1, y=45, label = "Fz", color = "black", size=3) +
 annotate("text", x=1, y=0, label = "Cz", color = "black", size=3) +
  annotate("text", x=1, y=-45, label = "Pz", color = "black", size=3)
plot6 <- topoplot(ga_diff,time_lim=c(275,425), chanLocs=chanlocs, contour=TRUE, interp_limit="skirt", chan_marker="none", scaling=scaling_factor, verbose=FALSE) +
 annotate("text", x=1, y=45, label = "Fz", color = "black", size=3) +
 annotate("text", x=1, y=0, label = "Cz", color = "black", size=3) +
  annotate("text", x=1, y=-45, label = "Pz", color = "black", size=3)

grid.arrange(textGrob(""), title_rewp, title_p300,
             title_acc,plot1,plot2,
             title_rej,plot3,plot4,
             title_diff,plot5,plot6,
             layout_matrix = rbind(seq(1,3), seq(4,6), seq(7,9), seq(10,12)),
             heights = c(0.1, 1, 1, 1),
             widths = c(0.2, 1, 1)
)
```

# Results

## Behavioral ratings

```{r, eval=FALSE}
post_task_table <- st(dplyr::select(df_BUDS_rating_it_pt, SP_debriefing_interested:SP_debriefing_nervous,SP_debriefing_socialmediause),
                      out="return")[,-c(5:8)] %>%
  mutate(Measure=c("Interested","Happy","Upset","Angry","Nervous","Social Media Use")) %>%
  dplyr::select(-Variable, -N) %>%
  dplyr::select(Measure, everything())
```

Of note, for low-value peers, participants rated being rejected as feeling *better* than being accepted.
Although seemingly counter-intuitive, previous work suggests that this is likely reflects participants feeling good that they were "right"---that they rejected the person who rejected them---and feeling guilty when they were "wrong"---rejected someone who accepted them [@distefanoComparisonElectrocorticalResponse2018; @quarmleyKnewYouWerent2019].

```{r, results='asis', include=TRUE}
spearman_brown <- spearman_brown_raw %>%
  select(-X,-AR_AA) %>%
  filter(`Time_windows`!="Fz 50-150ms")
spearman_brown[,1] <- c("RewP", "P300")
colnames(spearman_brown) <- c("ERP Component","HV Acceptance","HV Rejection","LV Acceptance","LV Rejection","HV Acceptance > \nHV Rejection")
spearman_brown <- t(spearman_brown)
colnames(spearman_brown) <- spearman_brown[1,]
spearman_brown <- spearman_brown[-1,]

apa_table(spearman_brown,
          note="HV= High-value peer, LV= Low-value peer",
          caption="Spearman Brown coefficients of split-half reliability for each ERP component")
```

```{r, results='asis', include=TRUE}
dependability <- data.frame(Condition = c("HV Acceptance","HV Rejection","LV Acceptance","LV Rejection"),
           RewP = c(13, 11, 11, 13),
           P300 = c(15, 13, 14, 14),
           RewP = c(0.81, 0.82, 0.82, 0.80),
           P300 = c(0.79, 0.80, 0.80, 0.80))

apa_table(dependability,
  col_spanners=list(
    "Trials for 70\\% dependability" = c(2, 3),
    "Overall dependability" = c(4, 5)),
  col.names = c("Condition","RewP","P300","RewP","P300"),
  caption="Number of trials needed to achieve at least 70% dependability, and overall dependability of RewP and P300 up to 25 trials each.",
  note = "HV = high-value peer, LV = low-value peer.",
  align = c("p{3.5cm}", rep("p{2cm}", 4))
)
```

## Including only those that reported belief in deception

### SES associations with RewP~resid~ and P300~resid~

```{r, eval=TRUE}
load(file=here("../data/BUDS_behavior.RData"))

df_150275_cz_dec <- df_150275_cz_rating %>%
  select(ID, SP_debriefing_deceived_f) %>%
  full_join(df_150275_cz, by="ID") %>%
  filter(SP_debriefing_deceived_f==1)

df_275425_pz_dec <- df_275425_pz_rating %>%
  select(ID, SP_debriefing_deceived_f) %>%
  full_join(df_275425_pz, by="ID") %>%
  filter(SP_debriefing_deceived_f==1)

ses_lm_dec <- function(data, y) {
  y <- enquo(y)

  model_formula <- formula(paste0(quo_name(y), "~ ADI_NATRANK_z + site + Age_z + demo_child_sex + StressCT_z + StressTH_z + IDAS_depression_z + IDAS_anxiety_z"))
  lm(model_formula, data = data)
}

rewp_aaar_model <- ses_lm_dec(df_150275_cz_dec, AA_AR_z)
p3_aaar_model <- ses_lm_dec(df_275425_pz_dec, AA_AR_z)

lm_results <- function(model, var) {
  tidy(model, conf.int=TRUE) %>%
    filter(term==var) %>%
    mutate(stat = paste0("$\\beta$=",round3(estimate), ", 95% CI= [",round3(conf.low), ", ", round3(conf.high),"], *p*=",round3(p.value))) %>%
    select(stat)
}
```

When excluding those who did not endorse deception, SES was still significantly, positively related to RewP~resid~ and P300~resid~ to acceptance (`r lm_results(rewp_aaar_model, "ADI_NATRANK_z")`, `r lm_results(p3_aaar_model, "ADI_NATRANK_z")`, respectively).

```{r}
df_150275_cz_ema_dec <- df_150275_cz_ema %>%
  group_by(ID,daysFrom,slot) %>%
  arrange(tm_start) %>%
  filter(row_number()==1) %>%
  arrange(ID,daysFrom,tm_start) %>%
  full_join(df_150275_cz_rating, by="ID")

df_275425_pz_ema_dec <- df_275425_pz_ema %>%
  group_by(ID,daysFrom,slot) %>%
  arrange(tm_start) %>%
  filter(row_number()==1) %>%
  arrange(ID,daysFrom,tm_start) %>%
  full_join(df_275425_pz_rating, by="ID")
```

### SES moderates association between RewP~resid~/P300~resid~ and negative affect

```{r}
model_150275_ema_na_dec <- glmmTMB(na_cubert ~ ADI_NATRANK_z*AA_AR_z + Age_z + demo_child_sex + site + (1 | ID),
                zi = ~ .,
  data = df_150275_cz_ema_dec,
  family=gaussian, REML=TRUE)

model_275425_ema_na_dec <- glmmTMB(na_cubert ~ ADI_NATRANK_z*AA_AR_z + Age_z + demo_child_sex + site + (1 | ID),
                                   zi = ~ .,
  data = df_275425_pz_ema_dec,
  family=gaussian, REML=TRUE)
```

```{r}
rewp_na_stat_dec <- c(broom.mixed::tidy(model_150275_ema_na_dec) %>% 
                    filter(effect == "fixed", component == "cond", term == "ADI_NATRANK_z:AA_AR_z"),
                  as.data.frame(confint(model_150275_ema_na_dec)) %>% 
                    rownames_to_column("row_name") %>% 
                    filter(row_name == "cond.ADI_NATRANK_z:AA_AR_z") %>% 
                       mutate(lower = round3(`2.5 %`), upper=round3(`97.5 %`)) %>% 
                       select(lower,upper))

p300_na_stat_dec <- c(broom.mixed::tidy(model_275425_ema_na_dec) %>%
                    filter(effect == "fixed", component == "cond", term == "ADI_NATRANK_z:AA_AR_z"),
                  as.data.frame(confint(model_275425_ema_na_dec)) %>%
                    rownames_to_column("row_name") %>%
                    filter(row_name == "cond.ADI_NATRANK_z:AA_AR_z") %>%
                       mutate(lower = round3(`2.5 %`), upper=round3(`97.5 %`)) %>%
                       select(lower,upper))
```

When excluding those who did not endorse deception, SES continued to significantly moderate the relationship between EMA-assessed negative affect and RewP~resid~ to acceptance ($\beta$=`r rewp_na_stat_dec$estimate`, 95% CI=[`r paste0(rewp_na_stat_dec$lower,", ", rewp_na_stat_dec$upper)`], *p*=`r round3(rewp_na_stat_dec$p.value)`), and the relationship between negative affect and the P300~resid~ to acceptance ($\beta$=`r p300_na_stat_dec$estimate`, 95% CI=[`r paste0(p300_na_stat_dec$lower,", ",p300_na_stat_dec$upper)`], *p*=`r round3(p300_na_stat_dec$p.value)`).

```{r}
## REWP
######## ACC > REJ ######## 
mean_ses <- mean(df_150275_cz_ema_dec$ADI_NATRANK_z, na.rm=TRUE)
sd_ses <- sd(df_150275_cz_ema_dec$ADI_NATRANK_z, na.rm=TRUE)
SES_list <- list(ADI_NATRANK_z=round(c(mean_ses + sd_ses,mean_ses - sd_ses),2)) 

m_rewp_acc_dec <- glmmTMB(na_cubert ~ ADI_NATRANK_z*AA_AR_z + Age_z + demo_child_sex + site + (1 | ID),
        zi = ~ .,
  data = df_150275_cz_ema_dec,
  family=gaussian, REML=TRUE)

m_rewp_acc_dec_ss <- emtrends(m_rewp_acc_dec, pairwise ~ADI_NATRANK_z, var="AA_AR_z",at=SES_list, adjust="none")|> test()

## P300
mean_ses <- mean(df_275425_pz_ema_dec$ADI_NATRANK_z, na.rm=TRUE)
sd_ses <- sd(df_275425_pz_ema_dec$ADI_NATRANK_z, na.rm=TRUE)
SES_list <- list(ADI_NATRANK_z=round(c(mean_ses + sd_ses,mean_ses - sd_ses),2)) 
######## ACC > REJ ######## 
m_p300_acc_dec <- glmmTMB(na_cubert ~ ADI_NATRANK_z*AA_AR_z + Age_z + demo_child_sex + site + (1 | ID),
        zi = ~ .,
  data = df_275425_pz_ema_dec,
  family=gaussian, REML=TRUE)

m_p300_acc_dec_ss <- emtrends(m_p300_acc_dec, pairwise ~ADI_NATRANK_z, var="AA_AR_z",at=SES_list, adjust="none")|> test()
```
Follow-up simple slope analyses excluding those who did not endorse deception were consistent with results: no simple slopes were significant for the SES x RewP~resid~ interaction (*p*$\ge$ `r round3(min(m_rewp_acc_dec_ss$emtrends[,6]))`), but were significant for the SES x P300~resid~ such that lower SES was associated with a more negative relationship between P300~resid~ to acceptance and subsequent negative affect (slope=`r round3(m_p300_acc_dec_ss$emtrends[2,2])`, *p*=`r round3(m_p300_acc_dec_ss$emtrends[2,6])`).

## Covarying for positive affect

### SES moderates association between RewP~resid~/P300~resid~ and negative affect

```{r}
# DOESN'T CONVERGE
# model_150275_ema_na_pa <- glmmTMB(na_cubert ~ ADI_NATRANK_z*AA_AR_z + Age_z + demo_child_sex + pa + site + (1 | ID),
#                 zi = ~ .,
#   data = df_150275_cz_ema,
#   family=gaussian, REML=TRUE)

model_275425_ema_na_pa <- glmmTMB(na_cubert ~ ADI_NATRANK_z*AA_AR_z + Age_c + demo_child_sex + pa + site + (1 | ID),
                                   zi = ~ .,
  data = df_275425_pz_ema,
  family=gaussian, REML=TRUE)

p300_na_pa_stat <- c(broom.mixed::tidy(model_275425_ema_na_pa) %>% 
                       filter(effect == "fixed", component == "cond", term == "ADI_NATRANK_z:AA_AR_z"),
                     as.data.frame(confint(model_275425_ema_na_pa)) %>% 
                       rownames_to_column("row_name") %>% 
                       filter(row_name == "cond.ADI_NATRANK_z:AA_AR_z") %>% 
                       mutate(lower = round3(`2.5 %`), upper=round3(`97.5 %`)) %>% 
                       select(lower,upper))
```

Models covarying for EMA reported positive affect did not converge for models testing SES moderating relationship between negative affect and RewP~resid~. However, SES continued to moderate the relationship between negative affect and P300~resid~ to acceptance ($\beta$=`r round3(p300_na_pa_stat$estimate)`, 95% CI=[`r paste0(p300_na_pa_stat$lower,", ",p300_na_pa_stat$upper)`], *p*=`r round3(p300_na_pa_stat$p.value)`).

# References

::: {#refs custom-style="Bibliography"}
:::
