---
title: "Data prep script: Grand averages and scalp topographies"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports and merges the self-report data from BUDS study: Bullying, Unsupportive family/peers, Discrimination, and Social feedback study using data from PREDICT project collaboration between Northwestern (PI: Shankman) and Columbia (PI: Auerbach).

# 1. Get Setup
## Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    # rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  # library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(Hmisc)
  library(MASS)
  library(papaja)
  library(eegUtils)
  library(tidyverse)  #plotting/cleaning, etc.
  library(workflowr)  #helps with workflow
here <- here::here
```

## Get the Working Directory
```{r}
  here::i_am("./management/data04_BUDS_GA.Rmd")
```

```{r}
load(file=here("data/BUDS_cleaning04_ga.RData"))
load(file=here("data/BUDS_cleaning04_gaplots.RData"))
```

## Load ERP data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r, eval=F, include=F}
subjects <- c(1000,
1001,
1004,
1006,
# 1010,
# 1012,
1014,
1017,
1021,
1022,
1023,
1024,
1025,
1026,
1027,
1029,
1030,
1031,
1033,
1035,
1036,
1037,
1039,
1040,
1043,
1044,
1046,
1047,
1048,
1049,
1050,
1052,
1053,
1054,
1055,
1057,
1058,
1059,
1060,
1061,
1063,
1064,
1065,
1066,
1067,
1068,
1069,
1070,
1071,
# 1072,
1074,
1075,
1077,
1078,
1079,
1080,
1081,
1082,
1084,
1085,
1086,
1087,
1088,
1089,
1090,
1091,
1094,
1095,
1096,
1098,
1099,
1100,
1101,
1102,
1103,
1104,
1105,
1106,
1107,
1108,
1109,
1110,
1111,
1112,
1114,
1115,
1117,
1118,
1119,
1120,
1121,
1122,
1123,
1124,
1125,
1126,
9001,
9003,
# 9004,
9006,
9007,
9008,
9010,
9013,
# 9014,
9015,
9017,
9018,
9019,
9020,
9021,
9022,
9024,
9026,
9027,
9028,
9030,
9031,
9033,
9034,
9035,
9037,
9038,
9039,
9040,
9042,
9043,
9044,
9045,
9046,
9048,
9049,
9051,
9052,
9053,
9055,
9057,
9059,
9060,
9061,
9062,
9063,
9067,
9068,
9069,
9070,
9072,
9075,
9076,
9077,
9078,
9079,
9080,
9081,
9082,
9083,
9084,
9085,
9087,
9088,
9089,
9091,
9092,
9093,
9094,
9096,
9097,
9098,
9099,
9100)

# channels <- c("AFz","C3","C4","CP1","CP2","CP5","CP6","CPz","Cz",
#               "F3","F4","F7","F8","FC1","FC2","FC5","FC6","FCz","FT10","FT9","Fp1","Fp2","Fz",
#               "Oz","P4","P7","P8","PO7","PO8","POz","Pz","TP10","TP9")

bad_150275 <- c(1025,
1055,
1084,
1090,
1101,
1122,
1124,
9015,
9017,
9019,
9035,
9051,
9057,
9081,
9082)

bad_275425 <- c(1055,
1084,
1090,
1101,
1124,
9015,
9017,
9019,
9035,
9051,
9081,
9082)

subjects <- setdiff(subjects, c(bad_150275,bad_275425))

library(eegUtils)
EEG <- import_set('./data/eeg_processing_fully_auto/DataPreprocessed/1000_continuous_icaed.set')
chanlocs <- EEG$chan_info
channels <- EEG$chan_info$electrode

df_ga <- as.data.frame(NA)
for (c in channels[-1]) {
  eval(parse(text=paste0('df_ga_',c,' <- as.data.frame(NA)')))
  for (s in subjects) {
   skip_to_next <- FALSE
   tryCatch({
    eval(parse(text=paste0(
     'df_',s,'_',c,' <- read.csv(here("./data/eeg_processing_fully_auto/Scripts/Results/cleaned_data/',s,'_',c,'_raw_erp.csv"), header=FALSE)
     colnames(df_',s,'_',c,') <- c("Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
     df_',s,'_',c,'$ID <- rep(',s,', 1100)
     df_',s,'_',c,'$electrode <- rep("',c,'", 1100)
     df_',s,'_',c,'$Time <- seq(-200,1998,2)
     df_ga_',c,' <- dplyr::bind_rows(df_ga_',c,', df_',s,'_',c,')')))
     cat(paste0("Subject ", s, " finished.\n"))
   }, error = function(e){skip_to_next <<- TRUE})
    if(skip_to_next) { next }
  }
  eval(parse(text=paste0('df_ga <- dplyr::bind_rows(df_ga, df_ga_',c,')')))
  cat(paste0("Component ", c, " finished.\n"))
}

eeg.map_for_plotting <- df_ga %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All), 
               values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  dplyr::filter(Time>150 & Time<350) %>%
  group_by(Condition, electrode) %>% #grouping required for summarise in the next step
  dplyr::summarise(amplitude = mean(ERP)) #calculate mean across subjects

topoplot(eeg.map_for_plotting, palette="RdBu", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")

save(EEG, df_ga, eeg.map_for_plotting, file=here("./data/eeg_map_for_plotting.RData"))
## ADD FC5
```

# Make grand averages
## Entire sample
```{r Make and plot grand averages, warning=FALSE, include=F}
df_ga_Cz_long <- df_ga_Cz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = Acc_Acc - Acc_Rej, # Create difference scores
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, AA_AR), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  group_by(Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_FCz_long <- df_ga_FCz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, data=., na.action=na.exclude)), # Create residualized differences
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, AA_AR), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  group_by(Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Fz_long <- df_ga_Fz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, data=., na.action=na.exclude)), # Create residualized differences
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, AA_AR), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  group_by(Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Pz_long <- df_ga_Pz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, data=., na.action=na.exclude)), # Create residualized differences
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, AA_AR), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  group_by(Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects
```

### By ADI median split

```{r, include=F}
load(file=here("data/BUDS_cleaning04_ga.RData"))
load(file=here("data/geocode_data_with_adi.RData"))

df_ga_Cz_adi_long <- df_ga_Cz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, data=., na.action=na.exclude)), # Create residualized differences
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, 
                      AA_AR, RA_RR, RR_RA, A_R, R_A), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  right_join(geocode_data_with_adi, by="ID", relationship="many-to-many") %>%
  mutate(adi_median_split = case_when(ADI_NATRANK_log < median(ADI_NATRANK_log, na.rm=T) ~ "low_ADI",
                                       ADI_NATRANK_log > median(ADI_NATRANK_log, na.rm=T) ~ "high_ADI")) %>%
  filter(complete.cases(ERP) & complete.cases(adi_median_split))

df_ga_Cz_adi_summarised <- df_ga_Cz_adi_long %>%
  group_by(adi_median_split,Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Cz_adi_wide <- df_ga_Cz_adi_long %>%
  pivot_wider(names_from=Condition, values_from=ERP) %>%
  group_by(adi_median_split,Time) %>%
  reframe(Acc_Acc=mean(Acc_Acc),
          Acc_Rej=mean(Acc_Rej),
          Rej_Acc=mean(Rej_Acc),
          Rej_Rej=mean(Rej_Rej),
          Acc_All=mean(Acc_All),
          Rej_All=mean(Rej_All),
         AA_AR = Acc_Acc - Acc_Rej, # Create subtraction based difference scores
         AR_AA = Acc_Rej - Acc_Acc,
         RA_RR = Rej_Acc - Rej_Rej,
         RR_RA = Rej_Rej - Rej_Acc,
         A_R = Acc_All - Rej_All,
         R_A = Rej_All - Acc_All) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, 
                      AA_AR, RA_RR, RR_RA, A_R, R_A), values_to ="ERP", names_to="Condition") %>%
  group_by(adi_median_split,Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Fz_adi_long <- df_ga_Fz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, data=., na.action=na.exclude)), # Create residualized differences
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, 
                      AA_AR, RA_RR, RR_RA, A_R, R_A), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  right_join(geocode_data_with_adi, by="ID", relationship="many-to-many") %>%
  mutate(adi_median_split = case_when(ADI_NATRANK_log < median(ADI_NATRANK_log, na.rm=T) ~ "low_ADI",
                                       ADI_NATRANK_log > median(ADI_NATRANK_log, na.rm=T) ~ "high_ADI")) %>%
  filter(complete.cases(ERP) & complete.cases(adi_median_split))

df_ga_Fz_adi_summarised <- df_ga_Fz_adi_long %>%
  group_by(adi_median_split,Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Fz_adi_wide <- df_ga_Fz_adi_long %>%
  pivot_wider(names_from=Condition, values_from=ERP) %>%
  group_by(adi_median_split,Time) %>%
  reframe(Acc_Acc=mean(Acc_Acc),
          Acc_Rej=mean(Acc_Rej),
          Rej_Acc=mean(Rej_Acc),
          Rej_Rej=mean(Rej_Rej),
          Acc_All=mean(Acc_All),
          Rej_All=mean(Rej_All),
         AA_AR = Acc_Acc - Acc_Rej, # Create subtraction based difference scores
         AR_AA = Acc_Rej - Acc_Acc,
         RA_RR = Rej_Acc - Rej_Rej,
         RR_RA = Rej_Rej - Rej_Acc,
         A_R = Acc_All - Rej_All,
         R_A = Rej_All - Acc_All) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, 
                      AA_AR, RA_RR, RR_RA, A_R, R_A), values_to ="ERP", names_to="Condition") %>%
  group_by(adi_median_split,Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Pz_adi_long <- df_ga_Pz %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  mutate(AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, data=., na.action=na.exclude)), # Create residualized differences
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, data=., na.action=na.exclude)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, data=., na.action=na.exclude)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, data=., na.action=na.exclude)),
         A_R = stdres(lm(Acc_All ~ Rej_All, data=., na.action=na.exclude)),
         R_A = stdres(lm(Rej_All ~ Acc_All, data=., na.action=na.exclude))) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, 
                      AA_AR, RA_RR, RR_RA, A_R, R_A), values_to ="ERP", names_to="Condition") %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  right_join(geocode_data_with_adi, by="ID", relationship="many-to-many") %>%
  mutate(adi_median_split = case_when(ADI_NATRANK_log < median(ADI_NATRANK_log, na.rm=T) ~ "low_ADI",
                                       ADI_NATRANK_log > median(ADI_NATRANK_log, na.rm=T) ~ "high_ADI")) %>%
  filter(complete.cases(ERP) & complete.cases(adi_median_split))

df_ga_Pz_adi_summarised <- df_ga_Pz_adi_long %>%
  group_by(adi_median_split,Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects

df_ga_Pz_adi_wide <- df_ga_Pz_adi_long %>%
  pivot_wider(names_from=Condition, values_from=ERP) %>%
  group_by(adi_median_split,Time) %>%
  reframe(Acc_Acc=mean(Acc_Acc),
          Acc_Rej=mean(Acc_Rej),
          Rej_Acc=mean(Rej_Acc),
          Rej_Rej=mean(Rej_Rej),
          Acc_All=mean(Acc_All),
          Rej_All=mean(Rej_All),
         AA_AR = Acc_Acc - Acc_Rej, # Create subtraction based difference scores
         AR_AA = Acc_Rej - Acc_Acc,
         RA_RR = Rej_Acc - Rej_Rej,
         RR_RA = Rej_Rej - Rej_Acc,
         A_R = Acc_All - Rej_All,
         R_A = Rej_All - Acc_All) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All, 
                      AA_AR, RA_RR, RR_RA, A_R, R_A), values_to ="ERP", names_to="Condition") %>%
  group_by(adi_median_split,Condition,Time) %>% #grouping required for summarise in the next step
  dplyr::summarise(grand_average = mean(ERP)) #calculate mean across subjects
```

### Scalp topography by ADI median split
```{r, eval=T, include=F}
load(file=here("./data/eeg_map_for_plotting.RData"))
EEG <- import_set(here('./data/eeg_processing_fully_auto/DataPreprocessed/1000_continuous_icaed.set'))
chanlocs <- EEG$chan_info
channels <- EEG$chan_info$electrode

select_topo_time_window_by_ADI <- function(data, start, end) {
  data %>%
  full_join(geocode_data_with_adi, by="ID", relationship="many-to-many") %>%
  mutate(adi_median_split = case_when(ADI_NATRANK_log < median(ADI_NATRANK_log, na.rm=T) ~ "low_ADI",
                                       ADI_NATRANK_log > median(ADI_NATRANK_log, na.rm=T) ~ "high_ADI")) %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All), 
               values_to ="ERP", names_to="Condition") %>%
  filter(complete.cases(ERP) & complete.cases(adi_median_split)) %>%
  arrange(ID,Condition,Time,adi_median_split) %>% #sort by Subid, Condition, and then Time
  dplyr::filter(Time>start & Time<end) %>%
  group_by(Condition, electrode, adi_median_split) %>% #grouping required for summarise in the next step
  dplyr::summarise(amplitude = mean(ERP)) #calculate mean across subjects
}

eeg.map_for_plotting_adi_50150 <- select_topo_time_window_by_ADI(df_ga, 50, 150)
eeg.map_for_plotting_adi_150275 <- select_topo_time_window_by_ADI(df_ga, 150, 275)
eeg.map_for_plotting_adi_275425 <- select_topo_time_window_by_ADI(df_ga, 275, 425)
```

# GA condition effects
```{r}
t.test(df_50150_cz$Acc_Acc, df_50150_cz$Acc_Rej, alternative="two.sided", paired="TRUE")
t.test(df_150275_cz$Acc_Acc, df_150275_cz$Acc_Rej, alternative="two.sided", paired="TRUE")
t.test(df_275425_cz$Acc_Acc, df_275425_cz$Acc_Rej, alternative="two.sided", paired="TRUE")
```

# Create plots
## AA > AR
```{r}
Cz_ga_aa_ar_plot <- ggplot(data=filter(df_ga_Cz_long, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  geom_line(linewidth=1) +
  xlim(-200,1000) +
  annotate("rect", xmin=50, xmax=150, ymin=-5, ymax=Inf, alpha=0.2, fill="orange") +
  annotate("rect", xmin=150, xmax=275, ymin=-5, ymax=Inf, alpha=0.2, fill="red") +
  annotate("rect", xmin=275, xmax=425, ymin=-5, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Cz") +
  theme_apa(base_size = 12) + theme(legend.position="top")

FCz_ga_aa_ar_plot <- ggplot(data=filter(df_ga_FCz_long, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  geom_line(linewidth=1) +
  xlim(-200,1000) +
  annotate("rect", xmin=50, xmax=150, ymin=-5, ymax=Inf, alpha=0.2, fill="orange") +
  annotate("rect", xmin=150, xmax=275, ymin=-5, ymax=Inf, alpha=0.2, fill="red") +
  annotate("rect", xmin=275, xmax=425, ymin=-5, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="FCz") +
  theme_apa(base_size = 12) + theme(legend.position="top")

Fz_ga_aa_ar_plot <- ggplot(data=filter(df_ga_Fz_long, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  geom_line(linewidth=1) +
  xlim(-200,1000) +
  annotate("rect", xmin=50, xmax=150, ymin=-5, ymax=Inf, alpha=0.2, fill="orange") +
  annotate("rect", xmin=150, xmax=275, ymin=-5, ymax=Inf, alpha=0.2, fill="red") +
  annotate("rect", xmin=275, xmax=425, ymin=-5, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Fz") +
  theme_apa(base_size = 12) + theme(legend.position="top")

Pz_ga_aa_ar_plot <- ggplot(data=filter(df_ga_Pz_long, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  geom_line(linewidth=1) +
  xlim(-200,1000) +
  annotate("rect", xmin=50, xmax=150, ymin=-5, ymax=Inf, alpha=0.2, fill="orange") +
  annotate("rect", xmin=150, xmax=275, ymin=-5, ymax=Inf, alpha=0.2, fill="red") +
  annotate("rect", xmin=275, xmax=425, ymin=-5, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Pz") +
  theme_apa(base_size = 12) + theme(legend.position="top")
```

```{r}
load(file=here("./data/eeg_map_for_plotting.RData"))
library(eegUtils)
EEG <- import_set(here('./data/eeg_processing_fully_auto/DataPreprocessed/1000_continuous_icaed.set'))
chanlocs <- EEG$chan_info
channels <- EEG$chan_info$electrode

select_topo_time_window <- function(data, start, end) {
  data %>%
  dplyr::select(-c("NA")) %>%
  filter(complete.cases(Acc_All)) %>%
  pivot_longer(cols=c(Acc_Acc, Acc_Rej, Rej_Acc, Rej_Rej, Acc_All, Rej_All), 
               values_to ="ERP", names_to="Condition") %>%
  filter(complete.cases(ERP)) %>%
  arrange(ID,Condition,Time) %>% #sort by Subid, Condition, and then Time
  dplyr::filter(Time>start & Time<end) %>%
  group_by(Condition, electrode) %>% #grouping required for summarise in the next step
  dplyr::summarise(amplitude = mean(ERP)) #calculate mean across subjects
}

eeg.map_for_plotting_50150 <- select_topo_time_window(df_ga, 50, 150)
eeg.map_for_plotting_150275 <- select_topo_time_window(df_ga, 150, 275)
eeg.map_for_plotting_275425 <- select_topo_time_window(df_ga, 275, 425)
```


```{r}
topoplot(eeg.map_for_plotting_50150, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(eeg.map_for_plotting_150275, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(eeg.map_for_plotting_275425, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")

Fz_ga_aa_ar_plot
FCz_ga_aa_ar_plot
Cz_ga_aa_ar_plot
Pz_ga_aa_ar_plot
```

# GA x ADI
## Waveforms
```{r}
ggplot(data=filter(df_ga_Cz_adi_wide, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 1000) +
  ylim( -5, 13) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=150, xmax=275, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Cz", title="High value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")

ggplot(data=filter(df_ga_Cz_adi_wide, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 1000) +
  ylim( -5, 13) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=275, xmax=425, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Cz", title="High value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")

ggplot(data=filter(df_ga_Cz_adi_wide, Condition=="Rej_Acc" | Condition=="Rej_Rej" | Condition=="RA_RR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 800) +
  ylim( -5, 13) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=150, xmax=350, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=12), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Rej_Acc","Rej_Rej","RA_RR"),
                     values=c("Rej_Acc"="green", "RA_RR"="black", "Rej_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Cz", title="Low value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")
```

```{r}
ggplot(data=filter(df_ga_Fz_adi_wide, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 800) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=100, xmax=450, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=10), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Fz", title="High value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")

ggplot(data=filter(df_ga_Fz_adi_wide, Condition=="Rej_Acc" | Condition=="Rej_Rej" | Condition=="RA_RR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 800) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=250, xmax=450, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=10), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Rej_Acc","Rej_Rej","RA_RR"),
                     values=c("Rej_Acc"="green", "RA_RR"="black", "Rej_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Fz", title="Low value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")
```

```{r}
ggplot(data=filter(df_ga_Pz_adi_wide, Condition=="Acc_Acc" | Condition=="Acc_Rej" | Condition=="AA_AR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 1000) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=275, xmax=425, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=10), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Acc_Acc","Acc_Rej","AA_AR"),
                     values=c("Acc_Acc"="green", "AA_AR"="black", "Acc_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Pz", title="High value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")

ggplot(data=filter(df_ga_Pz_adi_wide, Condition=="Rej_Acc" | Condition=="Rej_Rej" | Condition=="RA_RR"), aes(x=Time, y=grand_average, color=Condition)) +
  facet_wrap(~ adi_median_split) +
  xlim(-200, 800) +
  geom_line(linewidth=1) +
  annotate("rect", xmin=200, xmax=400, ymin=0, ymax=Inf, alpha=0.2, fill="blue") +
  geom_rect(aes(xmin=0, xmax=0, ymin=-5, ymax=10), color="black") +
  geom_rect(aes(xmin=-200, xmax=800, ymin=0, ymax=0), color="black") +
  scale_color_manual(breaks=c("Rej_Acc","Rej_Rej","RA_RR"),
                     values=c("Rej_Acc"="green", "RA_RR"="black", "Rej_Rej"="red"), 
                     labels=c("Acceptance","Rejection","Difference"), name=NULL) +
  labs(x="Time (ms)", y="Pz", title="Low value peers") +
  theme_apa(base_size = 12) + theme(legend.position="top")
```
High ADI participants show an enhanced P300 to high value rejection relative to acceptance.

## Scalp topographies
```{r, eval=FALSE}
topoplot(eeg.map_for_plotting_adi_150350, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_150350, adi_median_split=="high_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_150350, adi_median_split=="low_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")


topoplot(eeg.map_for_plotting_adi_250500, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_250500, adi_median_split=="high_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_250500, adi_median_split=="low_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")

topoplot(eeg.map_for_plotting_adi_200400, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_200400, adi_median_split=="high_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_200400, adi_median_split=="low_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")

topoplot(eeg.map_for_plotting_adi_150275, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_150275, adi_median_split=="high_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_150275, adi_median_split=="low_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")

topoplot(eeg.map_for_plotting_adi_50150, palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_50150, adi_median_split=="high_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
topoplot(filter(eeg.map_for_plotting_adi_50150, adi_median_split=="low_ADI"), palette="Spectral", chanLocs=chanlocs, contour=FALSE, interp_limit="head", chan_marker="name")
```

```{r}
save(df_ga_Cz, df_ga_FCz, df_ga_Fz, df_ga_Pz, file=here("data/BUDS_cleaning04_ga.RData"))
save(df_ga_Cz_long, df_ga_FCz_long, df_ga_Fz_long, df_ga_Pz_long, file=here("data/BUDS_cleaning04_gaplots.RData"))
save(eeg.map_for_plotting_adi_50150, eeg.map_for_plotting_adi_150275, eeg.map_for_plotting_adi_275425,
     eeg.map_for_plotting_50150, eeg.map_for_plotting_150275, eeg.map_for_plotting_275425, file=here("/data/BUDS_cleaning04_topo_windows.RData"))
```

