---
title: "Data prep script 3: Importing and combining ERP data with self-reported data"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script filter and scores the self-report data from BUDS study: Bullying, Unsupportive family/peers, Discrimination, and Social feedback study using data from PREDICT project collaboration between Northwestern (PI: Shankman) and Columbia (PI: Auerbach).

# Get Setup
## Clear everything & set width
```{r}
knitr::opts_chunk$set(set.seed(312), echo=FALSE, results='hide', message=FALSE, warning=FALSE, error=FALSE)
    options(width=80) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## Load Libraries
```{r}
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(MASS)
  library(papaja)     #generate APA documents
  library(Hmisc)
  library(misty)      #ordinal Cronbach's alpha
  library(lavaan)     #SEM
  library(papaja)
  library(pscl)       # for zero inflated models
  library(lme4)
  library(lmerTest)
  library(bbmle)
  library(marginaleffects)
  library(bestNormalize) # for normalizing data
  library(tidyverse)  #plotting/cleaning, etc.
  library(workflowr)  #helps with workflow

select <- dplyr::select
```

## Get the Working Directory
```{r}
  here::i_am("./management/data03_BUDS.Rmd")
```

## Load ERP data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r, eval=F}
subjects <- c(1000,
1001,
1004,
1006,
# 1010,
# 1012,
1014,
1017,
1021,
1022,
1023,
1024,
1025,
1026,
1027,
1029,
1030,
1031,
1033,
1035,
1036,
1037,
1039,
1040,
1043,
1044,
1046,
1047,
1048,
1049,
1050,
1052,
1053,
1054,
1055,
1057,
1058,
1059,
1060,
1061,
1063,
1064,
1065,
1066,
1067,
1068,
1069,
1070,
1071,
# 1072,
1074,
1075,
1077,
1078,
1079,
1080,
1081,
1082,
1084,
1085,
1086,
1087,
1088,
1089,
1090,
1091,
1094,
1095,
1096,
1098,
1099,
1100,
1101,
1102,
1103,
1104,
1105,
1106,
1107,
1108,
1109,
1110,
1111,
1112,
1114,
1115,
1117,
1118,
1119,
1120,
1121,
1122,
1123,
1124,
1125,
1126,
9001,
9003,
# 9004,
9006,
9007,
9008,
9010,
9013,
# 9014,
9015,
9017,
9018,
9019,
9020,
9021,
9022,
9024,
9026,
9027,
9028,
9030,
9031,
9033,
9034,
9035,
9037,
9038,
9039,
9040,
9042,
9043,
9044,
9045,
9046,
9048,
9049,
9051,
9052,
9053,
9055,
9057,
9059,
9060,
9061,
9062,
9063,
9067,
9068,
9069,
9070,
9072,
9075,
9076,
9077,
9078,
9079,
9080,
9081,
9082,
9083,
9084,
9085,
9087,
9088,
9089,
9091,
9092,
9093,
9094,
9096,
9097,
9098,
9099,
9100)

channels <- c("Fp1", "Fz", "F3", "F7", "FT9", "FC5", "FC1", 
              "C3", "TP9", "CP5", "CP1", 
              "Pz", "P3", "P7", "CPz", "Oz", "POz", "P4", "P8", "TP10", 
              "CP6", "CP2", "Cz", "C4", "AFz", 
              "FT10", "FC6", "FC2", "F4", "F8", "Fp2", "FCz")
time_windows <- c("150275", "50150", "275425", "150350", "200400", "250450", "4001000", "6001500")
time_windows <- c("150275", "50150", "275425")

for ( t in time_windows) {
  eval(parse(text=paste0('df_',t,' <- as.data.frame(NA)')))
  for (s in subjects) {
   eval(parse(text=paste0(
     'df_',s,'_',t,' <- as.data.frame(read.csv(here("./data/eeg_processing_fully_auto/Scripts/Results/subj_erp_Feedback/',s,'_component_',t,'.csv"), header=FALSE))
     colnames(df_',s,'_',t,') <- c("Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
     df_',s,'_',t,'$ID <- rep(',s,', 32)
     df_',s,'_',t,'$Channel <- channels
     df_',t,' <- bind_rows(df_',t,',df_',s,'_',t,')
     print(paste0("Done with subject ", s))'
     )))
  }
}

# Load Even and Odd trials
for (t in time_windows) {
  eval(parse(text=paste0('df_even_',t,' <- as.data.frame(NA)')))
  eval(parse(text=paste0('df_odd_',t,' <- as.data.frame(NA)')))
  print(paste0("***********Loading data from time window ",t," now***********"))
  for (s in subjects) {
    tryCatch({
   eval(parse(text=paste0('
     print(paste0("Load subject ",s,"_even data now"))
     df_even_',s,'_',t,' <- as.data.frame(read.delim(here("./data/eeg_processing_fully_auto/Scripts/Results/subj_erp_Feedback/split_half/even/',s,'_component_',t,'.txt"), header=TRUE))
     df_even_',s,'_',t,'$ID <- rep(',s,', 1)
     df_even_',t,' <- bind_rows(df_even_',t,',df_even_',s,'_',t,')'
     )))
   eval(parse(text=paste0('
   print(paste0("Load subject ",s,"_odd data now"))
     df_odd_',s,'_',t,' <- as.data.frame(read.delim(here("./data/eeg_processing_fully_auto/Scripts/Results/subj_erp_Feedback/split_half/odd/',s,'_component_',t,'.txt"), header=TRUE))
     df_odd_',s,'_',t,'$ID <- rep(',s,', 1)
     df_odd_',t,' <- bind_rows(df_odd_',t,',df_odd_',s,'_',t,')'
     )))
    }, error=function(e){cat("ERROR : For subject ",s, "; ", conditionMessage(e), "\n")})
  }
}

# load(file=here("./data/ERP_data.RData"))
save(df_275425, df_150350, df_250450, df_200400, df_4001000, df_6001500, df_150275, df_50150,
     df_even_150350, df_even_250450, df_even_200400, df_even_4001000, df_even_6001500, df_even_275425, df_even_150275, df_even_50150,
     df_odd_150350, df_odd_250450, df_odd_200400, df_odd_4001000, df_odd_6001500, df_odd_275425, df_odd_150275, df_odd_50150,
     file=here("./data/ERP_data.RData"))
```

## Load ERP data
```{r}
load(here("./data/ERP_data.RData"))
```

## Load self-report data
```{r}
load(here("data/BUDS_cleaning05.RData"))
BUDS_cleaning05$ID <- as.integer(as.character(BUDS_cleaning05$id_1_i))
BUDS_cleaning05 <- BUDS_cleaning05 %>%
  filter(!is.na(ID))
```

# Participant self-reported race
```{r}
# Import raw data files
nw_demo1 <- read.csv(here("../_rawdata/demo/nw/SP Demographics Child+Parent+18 Merged_9001-9042.csv"), colClasses="character", header=TRUE)[-c(1:2),] %>%
    dplyr::select(c(id_1_i, demo_child_gender, demo_child_sex, demo_child_race, demo_child_hispanic, demo_child_sex_or))
nw_demo2 <- read.csv(here("../_rawdata/demo/nw/SP Demographics 11.4.21_May 18, 2023_9042-9110.csv"), colClasses="character", header=TRUE)[-c(1:2),] %>%
    dplyr::select(c(id_1_i, demo_child_gender, demo_child_sex, demo_child_race, demo_child_hispanic, demo_child_sex_or))

nw_demo <- nw_demo1 %>%
  full_join(nw_demo2) %>% # merge two NW files together
  filter(complete.cases(demo_child_race)) # only keep participants with race data

cu_demo1 <- read.csv(here("../_rawdata/demo/cu/SP_Demographics (4.13.21)_November 1, 2021_12.34.csv"), colClasses="character", header=TRUE)[-c(1:2),] %>%
  filter(complete.cases(demo_child_race)) %>% # only keep participants with race data
  dplyr::select(c(id_1_i, demo_child_gender, demo_child_sex, demo_child_race, demo_child_hispanic, demo_child_sex_or))
cu_demo2 <- read.csv(here("../_rawdata/demo/cu/SP_Demographics (9.22.21)_July 18, 2023_08.08.csv"), colClasses="character", header=TRUE)[-c(1:2),] %>%
  filter(complete.cases(demo_child_race)) %>% # only keep participants with race data
  dplyr::select(c(id_1_i, demo_child_gender, demo_child_sex, demo_child_race, demo_child_hispanic, demo_child_sex_or))

cu_demo <- cu_demo1 %>%
  full_join(cu_demo2) %>% # merge two NW files together
  filter(complete.cases(demo_child_race)) # only keep participants with race data

# Convert ID variables to integers (as.character assures that values are not changed)
nw_demo <- nw_demo %>%
  mutate(ID = as.integer(as.character(id_1_i))) %>%
  dplyr::select(-id_1_i)
cu_demo <- cu_demo %>%
  mutate(ID = as.integer(as.character(id_1_i))) %>%
  dplyr::select(-id_1_i)

# Test whether there are any duplicate IDs
nw_demo[duplicated(nw_demo$ID)==TRUE,"ID"]
cu_demo[duplicated(cu_demo$ID)==TRUE,"ID"]

cu_demo <- cu_demo %>%
  distinct(ID, .keep_all=TRUE)

BUDS_cleaning05_demo <- rbind(cu_demo, nw_demo) %>%
  mutate(demo_child_gender = case_match(demo_child_gender,
                                        "1" ~ "Male", "2" ~ "Female", 
                                      "3" ~ "Trans male", "4" ~ "Trans female", 
                                      "5" ~ "Genderqueer/Gender non-conforming", 
                                      "6" ~ "Do not identify as any of these options", 
                                      "99" ~ "Prefer not to answer",
                                      .default=demo_child_gender),
         demo_child_sex = case_match(demo_child_sex,
                                     "1" ~ "male", "2" ~ "female",
                                     .default=demo_child_sex),
         demo_child_sex_or = case_match(demo_child_sex_or,
                                        "1" ~ "Heterosexual", "2" ~ "Gay or Lesbian",
                                        "3" ~ "Bisexual or pansexual", 
                                        "4" ~ "Asexual", "5" ~ "Not sure", 
                                        "99" ~ "Decline to state", "6" ~ "Other",
                                        .default=demo_child_sex_or),
         demo_child_race = case_match(demo_child_race,
                                      "1" ~ "American Indian/Alaska Native", 
                                      "2" ~ "Asian", 
                                      "3" ~ "Native Hawaiin or Other Pacific Islander", 
                                      "4" ~ "Black or African American", 
                                      "5" ~ "White", 
                                      "6" ~ "More than one race", 
                                      "99" ~ "Unknown or not reported",
                                      .default=demo_child_race),
         demo_child_hispanic = case_match(demo_child_hispanic, "Yes" ~ "Yes", "No" ~ "No",
                                          "0" ~ "No", "1" ~ "Yes")) %>%
  mutate(White_nonwhite = case_match(demo_child_race, c("White") ~ "White",
         c("More than one race", "Asian", "Black or African American", "American Indian/Alaska Native", "Native Hawaiian or Other Pacific Islander") ~ "Non_white")) %>%
  dplyr::select(c(ID, demo_child_gender, demo_child_sex, demo_child_race, demo_child_hispanic, White_nonwhite))
```

# Import 6 month followup
```{r, eval=FALSE}
# Import data from Columbia University
BUDS_cleaning01_columbia_6month <- read.csv(here("../_rawdata/Columbia/SP_Self-Report_6-Month (3.17.21)_August 14, 2023_12.21.csv"), header=TRUE)
var.labels = BUDS_cleaning01_columbia_6month[2,]; label(BUDS_cleaning01_columbia_6month) <- as.list(var.labels[match(names(BUDS_cleaning01_columbia_6month), names(var.labels))])

# Import data from Northwestern University
BUDS_cleaning01_nw_6month <- read.csv(here("../_rawdata/Northwestern/SP_Self-Report_6-Month_11.4.21_3.7.23.csv"), header=TRUE)
# Use the first row as the variable labels
var.labels = BUDS_cleaning01_nw_6month[1,]; label(BUDS_cleaning01_nw_6month) <- as.list(var.labels[match(names(BUDS_cleaning01_nw_6month), names(var.labels))])
BUDS_cleaning02_nw_6month <- BUDS_cleaning01_nw_6month[-(1),]; rm("BUDS_cleaning01_nw_6month")

BUDS_cleaning01_6month <- bind_rows(BUDS_cleaning01_columbia_6month, BUDS_cleaning02_nw_6month)
BUDS_cleaning01_6month$ID <- BUDS_cleaning01_6month$id_1_6
BUDS_cleaning02_6month <- BUDS_cleaning01_6month %>%
  filter(ID!="9075 - incorrect")
```

# Create IDAS score
## Baseline
```{r}
BUDS_cleaning05_idas <- as.data.frame(BUDS_cleaning05)[-c(1:2),] %>%
  select(ID,contains("idas")) %>%
  mutate_all(as.character())
idas <- colnames(BUDS_cleaning05_idas[,-1])
BUDS_cleaning05_idas_num <- BUDS_cleaning05_idas %>%
  mutate(across(all_of(c(idas)), ~ case_match(as.character(.), "1" ~ 1, "2" ~ 2, "3" ~ 3, "4" ~ 4, "5" ~ 5,
                                                       "Not at all" ~ 1,
                                                       "A little bit" ~ 2,
                                                       "Moderately" ~ 3,
                                                       "Quite a bit" ~ 4,
                                                       "Extremely" ~ 5)))

idas_dep <- c("idas_1_i","idas_2_i","idas_5_i","idas_6_i","idas_8_i","idas_9_i","idas_11_i","idas_13_i","idas_21_i","idas_26_i","idas_30_i","idas_31_i","idas_40_i","idas_48_i","idas_51_i","idas_52_i","idas_57_i","idas_61_i")
idas_wb <- c("idas_3_i","idas_10_i","idas_23_i","idas_27_i","idas_50_i","idas_53_i","idas_59_i","idas_64_i")
idas_panic <- c("idas_7_i","idas_16_i","idas_32_i","idas_39_i","idas_45_i","idas_49_i","idas_56_i","idas_58_i")
idas_sa <- c("idas_15_i","idas_18_i","idas_20_i","idas_41_i","idas_47_i","idas_99_i")
# idas_claus <- c("idas_74_i","idas_80_i","idas_84_i","idas_90_i","idas_94_i")

BUDS_cleaning05_idas_num$idas_27r = 6 - BUDS_cleaning05_idas_num$idas_27_i
BUDS_cleaning05_idas_num$idas_64r = 6 - BUDS_cleaning05_idas_num$idas_64_i
BUDS_cleaning05_idas_num$IDAS_depression = rowMeans(BUDS_cleaning05_idas_num[,idas_dep], na.rm=F)
BUDS_cleaning05_idas_num$IDAS_wellbeing = rowMeans(BUDS_cleaning05_idas_num[,idas_wb], na.rm=F)
BUDS_cleaning05_idas_num$IDAS_panic = rowMeans(BUDS_cleaning05_idas_num[,idas_panic], na.rm=F)
BUDS_cleaning05_idas_num$IDAS_sa = rowMeans(BUDS_cleaning05_idas_num[,idas_sa], na.rm=F)
BUDS_cleaning05_idas_num$IDAS_anxiety = rowMeans(BUDS_cleaning05_idas_num[,c(idas_panic,idas_sa)], na.rm=F)
# BUDS_cleaning05_idas_num$IDAS_claus = rowMeans(BUDS_cleaning05_idas_num[,idas_claus], na.rm=F)

cor.test(BUDS_cleaning05_idas_num$IDAS_panic, BUDS_cleaning05_idas_num$IDAS_sa)
hist(sqrt(BUDS_cleaning05_idas_num$IDAS_sa))

library(ggpubr)
shapiro.test(BUDS_cleaning05_idas_num$IDAS_depression)
BUDS_cleaning05_idas_num$IDAS_depression_sqrt <- sqrt(BUDS_cleaning05_idas_num$IDAS_depression)
BUDS_cleaning05_idas_num$IDAS_depression_log <- log(BUDS_cleaning05_idas_num$IDAS_depression)
BUDS_cleaning05_idas_num$IDAS_depression_rec <- 1/(BUDS_cleaning05_idas_num$IDAS_depression)

ggdensity(BUDS_cleaning05_idas_num, x = "IDAS_depression", fill = "lightgray", title = "IDAS_depression") +
  scale_x_continuous(limits = c(-1, 6)) +
  stat_overlay_normal_density(color = "red", linetype = "dashed")

shapiro.test(BUDS_cleaning05_idas_num$IDAS_wellbeing)
ggdensity(BUDS_cleaning05_idas_num, x = "IDAS_wellbeing", fill = "lightgray", title = "IDAS_wellbeing") +
  scale_x_continuous(limits = c(-1, 6)) +
  stat_overlay_normal_density(color = "red", linetype = "dashed")
```

## 6 month followup
```{r, eval=FALSE}
BUDS_cleaning05_idas_6month <- as.data.frame(BUDS_cleaning02_6month)[-c(1:2),] %>%
  select(ID,contains("idas")) %>%
  mutate_all(as.character())
idas <- colnames(BUDS_cleaning05_idas_6month[,-1])
BUDS_cleaning05_idas_num_6month <- BUDS_cleaning05_idas_6month %>%
  mutate(across(all_of(c(idas)), ~ case_match(as.character(.), "1" ~ 1, "2" ~ 2, "3" ~ 3, "4" ~ 4, "5" ~ 5,
                                                       "Not at all" ~ 1,
                                                       "A little bit" ~ 2,
                                                       "Moderately" ~ 3,
                                                       "Quite a bit" ~ 4,
                                                       "Extremely" ~ 5)))

idas_dep <- c("idas_1_6","idas_2_6","idas_5_6","idas_6_6","idas_8_6","idas_9_6","idas_11_6","idas_13_6","idas_21_6","idas_26_6","idas_27r","idas_30_6","idas_31_6","idas_40_6","idas_48_6","idas_51_6","idas_52_6","idas_57_6","idas_61_6","idas_64r")
idas_wb <- c("idas_3_6","idas_10_6","idas_23_6","idas_27_6","idas_50_6","idas_53_6","idas_59_6","idas_64_6")

BUDS_cleaning05_idas_num_6month$idas_27r = 6 - BUDS_cleaning05_idas_num_6month$idas_27_6
BUDS_cleaning05_idas_num_6month$idas_64r = 6 - BUDS_cleaning05_idas_num_6month$idas_64_6
BUDS_cleaning05_idas_num_6month$IDAS_depression_6month = rowMeans(BUDS_cleaning05_idas_num_6month[,idas_dep])
BUDS_cleaning05_idas_num_6month$IDAS_wellbeing_6month = rowMeans(BUDS_cleaning05_idas_num_6month[,idas_wb])
BUDS_cleaning05_idas_num_6month$ID <- unlabel(as.integer(BUDS_cleaning05_idas_num_6month$ID))

BUDS_cleaning05_idas_baseand6 <- left_join(BUDS_cleaning05_idas_num,
                                           dplyr::select(BUDS_cleaning05_idas_num_6month, ID, IDAS_depression_6month, IDAS_wellbeing_6month), by="ID") %>%
  filter(complete.cases(IDAS_depression_6month) & complete.cases(IDAS_depression)) %>%
  mutate(IDAS_depression_6month_r = rstandard(lm(IDAS_depression_6month ~ IDAS_depression, .)))
```

# Merge self-report and ERP data
```{r}
merge_self_report_with_erp <- function(data, electrode, self_report_data, demo_data, idas_data) {
  data %>%
  filter(Channel %in% electrode) %>%
  group_by(ID) %>%
  reframe(Acc_All = mean(Acc_All),
         Rej_All = mean(Rej_All),
         Acc_Acc = mean(Acc_Acc),
         Acc_Rej = mean(Acc_Rej),
         Rej_Acc = mean(Rej_Acc),
         Rej_Rej = mean(Rej_Rej)) %>%
  full_join(self_report_data, by="ID") %>%
  full_join(demo_data, by="ID") %>%
  dplyr::select(-contains(idas)) %>%
  left_join(idas_data, by="ID", relationship =
  "many-to-many") %>%
  filter(!is.na(Acc_All)) %>%
  ungroup() %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)),
         RA_RR = stdres(lm(Rej_Acc ~ Rej_Rej, .)),
         AA_RA = stdres(lm(Acc_Acc ~ Rej_Acc, .)),
         R_all = stdres(lm(Rej_All ~ Acc_All, .)),
         AR_AA = stdres(lm(Acc_Rej ~ Acc_Acc, .)),
         RR_RA = stdres(lm(Rej_Rej ~ Rej_Acc, .)),
         AA_AR_c = scale(AA_AR, center=T, scale=F),
         AA_AR_z = scale(AA_AR, center=T, scale=T),
         AR_AA_c = scale(AR_AA, center=T, scale=F),
         AR_AA_z = scale(AR_AA, center=T, scale=T))
}

merge_self_report_with_erp_long <- function(data) {
data %>%
  mutate(Like_Acc=Acc_Acc,
         Dislike_Acc=Rej_Acc,
         Like_Rej=Acc_Rej,
         Dislike_Rej=Rej_Rej,
         
         Like_Acc_c = scale(Acc_Acc, center=T, scale=F),
         Dislike_Acc_c = scale(Rej_Acc, center=T, scale=F),
         Like_Rej_c = scale(Acc_Rej, center=T, scale=F),
         Dislike_Rej_c = scale(Rej_Rej, center=T, scale=F)) %>%
  pivot_longer(cols=c("Like_Acc","Dislike_Acc","Like_Rej","Dislike_Rej"), names_to=c("Voting","Feedback"), names_sep="_", values_to="ERP")
}

df_275425_cz <- merge_self_report_with_erp(data=df_275425, electrode=c("Cz","CPz","Pz"), 
                                           self_report_data=BUDS_cleaning05, demo_data=BUDS_cleaning05_demo, idas_data=BUDS_cleaning05_idas_num)
df_275425_cz_long <- merge_self_report_with_erp_long(df_275425_cz)

df_150275_cz <- merge_self_report_with_erp(data=df_150275, electrode=c("Cz"), 
                                           self_report_data=BUDS_cleaning05, demo_data=BUDS_cleaning05_demo, idas_data=BUDS_cleaning05_idas_num)
df_150275_cz_long <- merge_self_report_with_erp_long(df_150275_cz)

df_50150_cz <- merge_self_report_with_erp(data=df_50150, electrode=c("Cz"), 
                                           self_report_data=BUDS_cleaning05, demo_data=BUDS_cleaning05_demo, idas_data=BUDS_cleaning05_idas_num)
df_50150_cz_long <- merge_self_report_with_erp_long(df_50150_cz)
```

## Split-half
### Even
```{r}
df_even_50150_cz <- df_even_50150 %>%
  dplyr::select(ID, contains("_Cz"))
colnames(df_even_50150_cz) <- c("ID","Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
df_even_50150_cz <- df_even_50150_cz[,1:7] %>%
  full_join(BUDS_cleaning05, by="ID") %>%
  filter(!is.na(Acc_All)) %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)))

df_even_150275_cz <- df_even_150275 %>%
  dplyr::select(ID, contains("_Cz"))
colnames(df_even_150275_cz) <- c("ID","Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
df_even_150275_cz <- df_even_150275_cz[,1:7] %>%
  full_join(BUDS_cleaning05, by="ID") %>%
  filter(!is.na(Acc_All)) %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)))

df_even_275425_cz <- df_even_275425 %>%
  dplyr::select(ID, contains("_Cz"))
colnames(df_even_275425_cz) <- c("ID","Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
df_even_275425_cz <- df_even_275425_cz[,1:7] %>%
  full_join(BUDS_cleaning05, by="ID") %>%
  filter(!is.na(Acc_All)) %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)))
```

### Odd
```{r}
df_odd_50150_cz <- df_odd_50150 %>%
  dplyr::select(ID, contains("_Cz"))
colnames(df_odd_50150_cz) <- c("ID","Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
df_odd_50150_cz <- df_odd_50150_cz[,1:7] %>%
  full_join(BUDS_cleaning05, by="ID") %>%
  filter(!is.na(Acc_All)) %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)))

df_odd_150275_cz <- df_odd_150275 %>%
  dplyr::select(ID, contains("_Cz"))
colnames(df_odd_150275_cz) <- c("ID","Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
df_odd_150275_cz <- df_odd_150275_cz[,1:7] %>%
  full_join(BUDS_cleaning05, by="ID") %>%
  filter(!is.na(Acc_All)) %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)))

df_odd_275425_cz <- df_odd_275425 %>%
  dplyr::select(ID, contains("_Cz"))
colnames(df_odd_275425_cz) <- c("ID","Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All")
df_odd_275425_cz <- df_odd_275425_cz[,1:7] %>%
  full_join(BUDS_cleaning05, by="ID") %>%
  filter(!is.na(Acc_All)) %>%
  mutate(A_all = stdres(lm(Acc_All ~ Rej_All, .)),
         AA_AR = stdres(lm(Acc_Acc ~ Acc_Rej, .)))
```

# Import Area Deprivation Index data
```{r, include=F}
# Import address info and sort by row number, to tie to subject number
geocode_data <- read.csv(here("../_rawdata/GeocodeResults_edited.csv"), header=F, colClasses='character') %>%
  mutate(V1=as.integer(as.character(V1))) %>%
  arrange(V1)
  # dplyr::slice(length(V1), 1:length(V1))
# geocode_data[1,1] <- 1
# Concatenate to make FIPS
geocode_data$FIPS <- as.numeric(as.character((paste0(geocode_data$V9,geocode_data$V10,geocode_data$V11,substr(geocode_data$V12,1,1)))))

# Import subject ID 
subj_rownumber <- openxlsx::read.xlsx(here("../_rawdata/Columbia/PREDICT_Addresses_formula.xlsx"))[,1:2]
geocode_data2 <- full_join(subj_rownumber,geocode_data, by="V1")
adi_codes <- read.csv(here("./data/ADI/national/US_2020_ADI_Census Block Group_v3.2.csv"))

geocode_data_with_adi <- left_join(geocode_data2, adi_codes, by="FIPS") %>%
  dplyr::select(c(ID,ADI_NATRANK,ADI_STATERNK)) %>%
  mutate(ADI_NATRANK = as.integer(as.character(ADI_NATRANK)),
         ADI_NATRANK_log = log(ADI_NATRANK))

df_275425_cz <- left_join(df_275425_cz, geocode_data_with_adi, by="ID") %>%
  filter(complete.cases(AA_AR)) %>%
  mutate(ADI_NATRANK_log_c = scale(center=TRUE, scale=FALSE, ADI_NATRANK_log),
         ADI_NATRANK_log_z = scale(center=TRUE, scale=TRUE, ADI_NATRANK_log))
df_150275_cz <- left_join(df_150275_cz, geocode_data_with_adi, by="ID") %>%
  filter(complete.cases(AA_AR)) %>%
  mutate(ADI_NATRANK_log_c = scale(center=TRUE, scale=FALSE, ADI_NATRANK_log),
         ADI_NATRANK_log_z = scale(center=TRUE, scale=TRUE, ADI_NATRANK_log))
df_50150_cz <- left_join(df_50150_cz, geocode_data_with_adi, by="ID") %>%
  filter(complete.cases(AA_AR)) %>%
  mutate(ADI_NATRANK_log_c = scale(center=TRUE, scale=FALSE, ADI_NATRANK_log),
         ADI_NATRANK_log_z = scale(center=TRUE, scale=TRUE, ADI_NATRANK_log))

corr.test(df_150275_cz$AA_AR, df_275425_cz$AA_AR)
corr.test(df_150275_cz$Acc_Acc, df_275425_cz$Acc_Rej)

df_275425_cz_long <- left_join(df_275425_cz_long, geocode_data_with_adi, by="ID") %>%
        mutate(site = case_match(as.character(id_2_i), "CUMC" ~ "Columbia",
                                   "2" ~ "Northwestern",
                                   NA ~ NA)) %>%
  group_by(Voting, Feedback) %>%
  mutate(ADI_NATRANK_log_c = scale(center=TRUE, scale=FALSE, ADI_NATRANK_log),
         ADI_NATRANK_log_z = scale(center=TRUE, scale=TRUE, ADI_NATRANK_log))
df_150275_cz_long <- left_join(df_150275_cz_long, geocode_data_with_adi, by="ID") %>%
        mutate(site = case_match(as.character(id_2_i), "CUMC" ~ "Columbia",
                                   "2" ~ "Northwestern",
                                   NA ~ NA)) %>%
  group_by(Voting, Feedback) %>%
  mutate(ADI_NATRANK_log_c = scale(center=TRUE, scale=FALSE, ADI_NATRANK_log),
         ADI_NATRANK_log_z = scale(center=TRUE, scale=TRUE, ADI_NATRANK_log))
df_50150_cz_long <- left_join(df_50150_cz_long, geocode_data_with_adi, by="ID") %>%
        mutate(site = case_match(as.character(id_2_i), "CUMC" ~ "Columbia",
                                   "2" ~ "Northwestern",
                                   NA ~ NA)) %>%
  group_by(Voting, Feedback) %>%
  mutate(ADI_NATRANK_log_c = scale(center=TRUE, scale=FALSE, ADI_NATRANK_log),
         ADI_NATRANK_log_z = scale(center=TRUE, scale=TRUE, ADI_NATRANK_log))
```

# STRAIN
```{r}
load(here("data/BUDS_cleaning02_with_strain.RData"))
BUDS_cleaning02_with_strain$ID <- as.integer(as.character(BUDS_cleaning02_with_strain$id_1_i))

df_275425_cz_strain <- df_275425_cz %>%
  full_join(BUDS_cleaning02_with_strain, by="ID")

df_150275_cz_strain <- df_150275_cz %>%
  full_join(BUDS_cleaning02_with_strain, by="ID")

df_50150_cz_strain <- df_50150_cz %>%
  full_join(BUDS_cleaning02_with_strain, by="ID")

df_275425_cz_long_strain <- df_275425_cz_long %>%
  full_join(BUDS_cleaning02_with_strain, by="ID", relationship = "many-to-many")

df_150275_cz_long_strain <- df_150275_cz_long %>%
  full_join(BUDS_cleaning02_with_strain, by="ID", relationship = "many-to-many")

df_50150_cz_long_strain <- df_50150_cz_long %>%
  full_join(BUDS_cleaning02_with_strain, by="ID", relationship = "many-to-many")
```

# Split-half
```{r}
library(confintr)
compute_split_half <- function(time_window) {
  for (contrast in c("Acc_Acc","Acc_Rej","Rej_Acc","Rej_Rej","Acc_All","Rej_All","A_all","AA_AR")){
    eval(parse(text=paste0('
    r_half_',time_window,'',contrast,' <- cor(df_even_',time_window,'_cz$',contrast,', df_odd_',time_window,'_cz$',contrast,', method="spearman", use="pairwise")
    r_half_',time_window,'ci_',contrast,' <- ci_cor(df_even_',time_window,'_cz$',contrast,', df_odd_',time_window,'_cz$',contrast,', method="spearman", type = "bootstrap", R=1000)
    r_sb_',time_window,'_cilower_',contrast,' <<- (2*r_half_',time_window,'ci_',contrast,'$interval[1])/(1+r_half_',time_window,'ci_',contrast,'$interval[1])
    r_sb_',time_window,'_ciupper_',contrast,' <<- (2*r_half_',time_window,'ci_',contrast,'$interval[2])/(1+r_half_',time_window,'ci_',contrast,'$interval[2])
    r_sb_',time_window,'_',contrast,' <<- (2*r_half_',time_window,'',contrast,')/(1+r_half_',time_window,'',contrast,')
    ')))
}
}

compute_split_half("50150")
compute_split_half("150275")
compute_split_half("275425")

spearman_brown <- data.frame(Time_windows=c("Cz 50-150ms","Cz 150-275ms","Cz 275-425ms"))
spearman_brown$Acc_Acc <- c(r_sb_50150_Acc_Acc,r_sb_150275_Acc_Acc,r_sb_275425_Acc_Acc)
spearman_brown$Acc_Rej <- c(r_sb_50150_Acc_Rej,r_sb_150275_Acc_Rej,r_sb_275425_Acc_Rej)
spearman_brown$Rej_Acc <- c(r_sb_50150_Rej_Acc,r_sb_150275_Rej_Acc,r_sb_275425_Rej_Acc)
spearman_brown$Rej_Rej <- c(r_sb_50150_Rej_Rej,r_sb_150275_Rej_Rej,r_sb_275425_Rej_Rej)
spearman_brown[,2:5] <- round(spearman_brown[,2:5],2)
```

# Save files
```{r}
save(df_150275_cz, df_150275_cz_long,
     df_50150_cz, df_50150_cz_long,
     df_275425_cz, df_275425_cz_long,
     df_150275_cz_strain, df_150275_cz_long_strain,
     df_50150_cz_strain, df_50150_cz_long_strain,
     df_275425_cz_strain, df_275425_cz_long_strain,
     file=here("./data/BUDS_df_ERP.RData"))

save(geocode_data_with_adi, file=here("./data/geocode_data_with_adi.RData"))

save(df_even_50150_cz, df_even_150275_cz, df_even_275425_cz, file=here("./data/BUDS_split_half_even.RData"))
save(df_odd_50150_cz, df_odd_150275_cz, df_odd_275425_cz, file=here("./data/BUDS_split_half_odd.RData"))

# write.csv(spearman_brown, here("tables/spearman_brown.csv"))
```
